Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-05-21 paper.tex
small changes

@@

%Variants of Hadoop have been implemented for scientific
%applications such as Marissa~\cite{marissa} addressing HDFS
%accessibility and performance for applications that are not ported for
%Java. Our approach differs from Hadoop in that we use the highly general
%Swift programming model to generate and distribute tasks, while using
%Swift-automated staging or ad hoc data access techniques depending on
%the underlying storage system.  As shown in our application results,
%this provides high levels of generality and flexibility with respect
%to the workflow pattern, application domain, and underlying
%infrastructure.

>>>>

Amazon S3 offers lifecycle management for versioned objects: https://aws.amazon.com/blogs/aws/amazon-s3-lifecycle-management-update

@@

Recently developed systems for deduplication of data in the clous like
liquid~\cite{liquid:2014} are closely related to our work.

Variants of Hadoop have been implemented for scientific
applications such as Marissa~\cite{marissa} addressing HDFS
accessibility and performance for applications that are not ported for
Java. Our approach differs from Hadoop in that we use the highly general
Swift programming model to generate and distribute tasks, while using
Swift-automated staging or ad hoc data access techniques depending on
the underlying storage system.  As shown in our application results,
this provides high levels of generality and flexibility with respect
to the workflow pattern, application domain, and underlying
infrastructure.
